The expected shape of the Milky Way's Dark Matter halo

### 2018-09-17 Paper/paper.tex
More references

One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$. This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg et al. 1999, Vera-Ciro et al. 2011}. The general concensus in numerical simulations \citep[e.g.][]{Dubinski and Calberg 1991,Hayashi et al. 2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al. 2006}. Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood et al. 2006,Vera-Ciro et al. 2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\

@@

In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e. a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{Law_and_Majewski_2010,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,Law_and_Majewski_2009,Deg,BanerjeeChanda}. However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\

Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos. Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}. Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-). Other works of this type?\\

>>>>

One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$ \citet{Frenk_et_al._1988}. This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg_et_al._1999,Vera-Ciro_et_al._2011}. The general concensus in numerical simulations \citep[e.g.][]{Dubinski_and_Calberg_1991,Hayashi_et_al._2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood_et_al._2006}. Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood_et_al._2006,Vera-Ciro_et_al._2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\

@@

In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e. a=b>c) configurations at small distances around \~ $<20kpc$ \citep[see][]{Olling_and_Merrifield_2000,Law_and_Majewski_2010,Loebman_et_al._2012,Vera-Ciro_and_Helmi_2013,Bovy_et_el._2016}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Law_and_Majewski_2009,Banerjee_and_Chanda_2011,Deg_and_Widrow_2013,Vera-Ciro_and_Helmi_2013}. However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{Bowden_et_al._2016,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{Pearson_et_al._2015, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{Ibata_et_al._2013}.\\

Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos. Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{Scannapieco_et_al._2009,Yurin_and_Springel_2015}. Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-). Other works of this type?\\
